### 2016-09-01 latex/paper.tex
Rewrite final Intro paragraph

The buckling tension is controlled by the geometric and material properties of the wheel. The wheel designer may wish to achieve the stiffest and strongest wheel for a given size and weight by tuning parameters such as spoke count, spoke angle, rim width and depth, and material. Here we will answer the question of precisely how each of these factors affects the maximum safe tension in order to guide rational wheel design and component selection.

@@

\begin{table}[ht!]
\caption{A partial list of symbols is given below. Other symbols are defined in-place or not re-used.}
\begin{tabular}{c|p{12cm}}
\hline
\textit{\textbf{Term}} & \textit{\textbf{Definition}} \\
\hline
$n_s$		& Number of spokes\\
$E_s, A_s$	& Spoke Young's modulus and cross-sectional area\\
$l$			& Spoke length\\
$\alpha$	& Out-of-plane spoke angle--wall angle of a hypothetical ``cone'' of spokes\\
$\beta$		& In-plane spoke angle--measured between the in-plane projection of the spoke and
			  a radius of the wheel\\
$\n$		& Unit vector aligned with the spoke axis\\
$\nn,\nnn$	& Two unit vectors perpendicular to the spoke axis\\
$\bm{f}$	& Force exerted by a spoke on the rim\\
$\bar{\bm{f}}$& Distributed force (per-unit-length) exerted by the spokes on the rim\\
$f_1, f_2,f_3$ & Vector components of $\bm{f}$\\
$\bm{k}_f$	& Stiffness matrix for a single spoke\\
$\bar{\bm{k}}$ & Equivalent stiffness per-unit-length of the spoke system. $\bar{\bm{k}} = \bar{\bm{k}}^{el} + \bar{\bm{k}}^{tens}$\\
$\bar{\bm{k}}^{el},\bar{\bm{k}}^{tens}$ & Parts of $\bar{\bm{k}}$ proportional to $E_sA_s$ and $T$, respectively\\
$\bar{k}_{ij}$ & Matrix components of $\bar{\bm{k}}$, where $i,j\rightarrow u,w,v$ \\
$\e,\ee,\eee$ & Coordinate axes defined at the rim shear center\\
$s$			& Arc-length coordinate along the rim\\
$\kappa_1,\kappa_2,\kappa_3$ & Spatial curvature of the rim\\
$\bm{u}$	& Displacement of the rim shear center\\
$u,v,w$		& Vector components of $\bm{u}$ in the \e{}, \ee{}, \eee{} directions.\\
$\phi$		& Rotation of the rim cross-section about the $\hat{\bm{e}}_3$ axis.\\
$\delta u, \delta \phi$ & Virtual displacement and rotation\\
$\delta u_n, \delta\phi_n$ & Buckling mode coefficients\\
$n$			& Buckling mode number\\
$U_{rim}$	& Strain energy in the rim due to buckling\\
$V_{rim}$	& Virtual work of internal forces in the rim\\
$U_{spokes}$& Strain energy in the spokes due to buckling\\
$T$			& Tension in a spoke\\
$T_{cn}$	& Critical spoke tension for the $n$th mode\\
$T_c$		& Critical buckling tension (minimum of $T_{cn}$ over all modes)\\
$T_e$		& ``Euler'' tension--tension which would produce an axial force in the rim
			  equal to the buckling load for a straight beam-column of length $2\pi R$\\
$R$			& Rim radius measured from the rim shear center\\
$E, G$		& Rim Young's modulus and shear modulus\\
$I_{11}$	& Second moment of area of the rim in the lateral direction\\
$J$			& Rim torsion constant\\
$I_w$		& Rim warping constant\\
$\widetilde{GJ}$ & Effective torsional rigidity including both Saint-Venant torsion and warping\\
$\tilde{\mu}$ & Ratio of effective torsional rigidity to bending rigidity: $\widetilde{GJ}/EI_{11}$\\
$\lambda$	& Ratio of spoke system lateral stiffness to rim effective bending stiffness \\
\hline
\end{tabular}
\end{table}

>>>>

The spoke tension to cause buckling is affected by the spoke axial stiffness, spoke count, and spoke bracing angle. It is also strongly affected by the rim lateral bending stiffness, torsional stiffness, and radius. Our aim here is to provide formulas to predict the maximum allowable tension in terms of these properties and offer practical design rules to select the properties to achieve a desired maximum tension.

@@

\begin{table}[ht!]
\caption{A partial list of symbols used in this paper is given below. Other symbols are defined in-place or not re-used.}
\begin{tabular}{c|p{12cm}}
\hline
\textit{\textbf{Term}} & \textit{\textbf{Definition}} \\
\hline
$n_s$		& Number of spokes\\
$E_s, A_s$	& Spoke Young's modulus and cross-sectional area\\
$l$			& Spoke length\\
$\alpha$	& Out-of-plane spoke angle--wall angle of a hypothetical ``cone'' of spokes\\
$\beta$		& In-plane spoke angle--measured between the in-plane projection of the spoke and
			  a radius of the wheel\\
$\n$		& Unit vector aligned with the spoke axis\\
$\nn,\nnn$	& Two unit vectors perpendicular to the spoke axis\\
$\bm{f}$	& Force exerted by a spoke on the rim\\
$\bar{\bm{f}}$& Distributed force (per-unit-length) exerted by the spokes on the rim\\
$f_1, f_2,f_3$ & Vector components of $\bm{f}$\\
$\bm{k}_f$	& Stiffness matrix for a single spoke\\
$\bar{\bm{k}}$ & Equivalent stiffness per-unit-length of the spoke system. $\bar{\bm{k}} = \bar{\bm{k}}^{el} + \bar{\bm{k}}^{tens}$\\
$\bar{\bm{k}}^{el},\bar{\bm{k}}^{tens}$ & Parts of $\bar{\bm{k}}$ proportional to $E_sA_s$ and $T$, respectively\\
$\bar{k}_{ij}$ & Matrix components of $\bar{\bm{k}}$, where $i,j\rightarrow u,w,v$ \\
$\e,\ee,\eee$ & Coordinate axes defined at the rim shear center\\
$s$			& Arc-length coordinate along the rim\\
$\kappa_1,\kappa_2,\kappa_3$ & Spatial curvature of the rim\\
$\bm{u}$	& Displacement of the rim shear center\\
$u,v,w$		& Vector components of $\bm{u}$ in the \e{}, \ee{}, \eee{} directions.\\
$\phi$		& Rotation of the rim cross-section about the $\hat{\bm{e}}_3$ axis.\\
$\delta u, \delta \phi$ & Virtual displacement and rotation\\
$\delta u_n, \delta\phi_n$ & Buckling mode coefficients\\
$n$			& Buckling mode number\\
$U_{rim}$	& Strain energy in the rim due to buckling\\
$V_{rim}$	& Virtual work of internal forces in the rim\\
$U_{spokes}$& Strain energy in the spokes due to buckling\\
$T$			& Tension in a spoke\\
$T_{cn}$	& Critical spoke tension for the $n$th mode\\
$T_c$		& Critical buckling tension (minimum of $T_{cn}$ over all modes)\\
$T_e$		& ``Euler'' tension--tension which would produce an axial force in the rim
			  equal to the buckling load for a straight beam-column of length $2\pi R$\\
$R$			& Rim radius measured from the rim shear center\\
$E, G$		& Rim Young's modulus and shear modulus\\
$I_{11}$	& Second moment of area of the rim in the lateral direction\\
$J$			& Rim torsion constant\\
$I_w$		& Rim warping constant\\
$\widetilde{GJ}$ & Effective torsional rigidity including both Saint-Venant torsion and warping\\
$\tilde{\mu}$ & Ratio of effective torsional rigidity to bending rigidity: $\widetilde{GJ}/EI_{11}$\\
$\lambda$	& Ratio of spoke system lateral stiffness to rim effective bending stiffness \\
\hline
\end{tabular}
\end{table}
